# Simulation Experiment

Here, we will (1) simulate FR data, (2) fit FR models to the simulated data, and (3) select the "best fit" model using AIC, Juliano's, visual inspection, generalized FR model w/ scaling exponent.

Empirically, Grimm et al. conducted three experiments, within which three, three, and two treatments we applied, resulting in eight data sets. From here, Rogers' Type II and Hassell's Type III functional response models were fit to the data. We will use estimated parameter values from each experiment and treatment to simulate each of these two models, 1000 times.

Rogers' Type II FR:

$$
N_e=N_0(1-exp^{a(N_eh-T)})
$$

Where $N_e$ is the number of prey eaten, $N_0$​ is the initial number of prey, and $a$, $h$, and $T$ are the attack rate, handling time and the total time available, respectively.

Hassell's Type III FR:

$$
N_e=N_0(1-exp^{bN_0\frac{N_eh-T}{1+cN_0}})
$$

Where $b$, and $c$ are free parameters.

## Set-Up

```{r}
library(frair); library(lamW); library(tidyverse); library(here)
```

```{r}
## Rogers' Type II Model
RogersII <- function(N0, a, h, time){
  N0 - lamW::lambertW0(a * h * N0 * exp(-a * (time - h * N0)))/(a * h)
}

## Hassell's Type III Model
HassellIII <- function(N0, b, c, h, time){
  a <- b*N0/(1 + c*N0)
  N0 - lamW::lambertW0(a * h * N0 * exp(-a * (time - h * N0)))/(a * h)
}

# Test
N0s <- seq(5, 150, 5)
Outputs <- c()
for (i in 1:length(N0s)){
  Outputs[i] <- RogersII(N0s[i], 0.2, 0.2, 2)
}
plot(N0s, Outputs)

N0s <- seq(5, 150, 5)
Outputs <- c()
for (i in 1:length(N0s)){
  Outputs[i] <- HassellIII(N0s[i], 0.1, 0.1, 0.02, 2)
}
plot(N0s, Outputs)
```

Parameter Estimates by Experiment and Treatment:

...

## Simulations

### Experiment #1

#### Treatment: Low

##### Rogers' Type II FR Model

```{r}
# Initial Densities

N0 <- c(4, 6, 10, 20, 60, 90, 120)

# Simulations

set.seed(123)
a.vec <- sample(seq(0.489, 3.598, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.055, 0.094, 0.001), 1000, replace = TRUE)
Ex1.TLow.II.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.TLow.II.Unif[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

set.seed(123)
a.vec <- rlnorm(1000, mean = log(1.704), sd = log(2)) 
h.vec <- rlnorm(1000, mean = log(0.072), sd = log(2)) 
Ex1.TLow.II.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.TLow.II.Norm[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 1, Low Treatment: Rogers' Type II FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 50))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.TLow.II.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 1, Low Treatment: Rogers' Type II FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 150))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.TLow.II.Norm[[i]][j])
  }
}
```

##### Hassell's Type III FR Model

[***NA***]{.underline}

#### Treatment: Medium

##### Rogers' Type II FR Model

```{r}
# Initial Densities

N0 <- c(4, 6, 10, 20, 60, 90, 120)

# Simulations

set.seed(123)
a.vec <- sample(seq(0.706, 1.458, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.033, 0.059, 0.001), 1000, replace = TRUE)
Ex1.TMed.II.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.TMed.II.Unif[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

set.seed(123)
a.vec <- rlnorm(1000, mean = log(1.036), sd = log(2)) 
h.vec <- rlnorm(1000, mean = log(0.046), sd = log(2)) 
Ex1.TMed.II.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.TMed.II.Norm[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 1, Medium Treatment: Rogers' Type II FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 50))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.TMed.II.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 1, Medium Treatment: Rogers' Type II FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 150))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.TMed.II.Norm[[i]][j])
  }
}
```

##### Hassell's Type III FR Model

```{r}
# Initial Densities

N0 <- c(4, 6, 10, 20, 60, 90, 120)

# Simulations

set.seed(123)
b.vec <- sample(seq(0.218, 1686863.823/100000, 0.001), 1000, replace = TRUE) 
c.vec <- sample(seq(0.049, 1796176.396/100000, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.033, 0.06, 0.001), 1000, replace = TRUE)
Ex1.TMed.III.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.TMed.III.Unif[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

set.seed(123)
b.vec <- rlnorm(1000, mean = log(5.303), sd = log(2))
c.vec <- rlnorm(1000, mean = log(5.000), sd = log(2))
h.vec <- rlnorm(1000, mean = log(0.046), sd = log(2))
Ex1.TMed.III.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.TMed.III.Norm[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 1, Medium Treatment: Hassell's Type III FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 80))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.TMed.III.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 1, Medium Treatment: Hassell's Type III FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 150))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.TMed.III.Norm[[i]][j])
  }
}
```

#### Treatment: High

##### Rogers' Type II FR Model

```{r}
# Initial Densities

N0 <- c(4, 6, 10, 20, 60, 90, 120)

# Simulations

set.seed(123)
a.vec <- sample(seq(0.224, 1.055, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.028, 0.091, 0.001), 1000, replace = TRUE)
Ex1.THigh.II.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.THigh.II.Unif[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

set.seed(123)
a.vec <- rlnorm(1000, mean = log(0.607), sd = log(2)) 
h.vec <- rlnorm(1000, mean = log(0.055), sd = log(2)) 
Ex1.THigh.II.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.THigh.II.Norm[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 1, High Treatment: Rogers' Type II FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 60))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.THigh.II.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 1, High Treatment: Rogers' Type II FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 100))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.THigh.II.Norm[[i]][j])
  }
}
```

##### Hassell's Type III FR Model

```{r}
# Initial Densities

N0 <- c(4, 6, 10, 20, 60, 90, 120)

# Simulations

set.seed(123)
b.vec <- sample(seq(0.079, 1072285.537/1000000, 0.001), 1000, replace = TRUE) 
c.vec <- sample(seq(0.000, 2227240.993/1000000, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.008, 0.088, 0.001), 1000, replace = TRUE)
Ex1.THigh.III.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.THigh.III.Unif[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

set.seed(123)
b.vec <- rlnorm(1000, mean = log(0.537), sd = log(2))
c.vec <- rlnorm(1000, mean = log(0.758), sd = log(2))
h.vec <- rlnorm(1000, mean = log(0.058), sd = log(2))
Ex1.THigh.III.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex1.THigh.III.Norm[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 1, High Treatment: Hassell's Type III FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 150))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.THigh.III.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 1, High Treatment: Hassell's Type III FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 120), ylim = c(0, 150))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex1.THigh.III.Norm[[i]][j])
  }
}
```

### Experiment #2

#### Treatment: Low

##### Rogers' Type II FR Model

```{r}
# Initial Densities

N0 <- c(2, 3, 5, 10, 20, 30, 50)

# Simulations

set.seed(123)
a.vec <- sample(seq(0.262, 0.752, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.000, 0.132, 0.001), 1000, replace = TRUE)
Ex2.TLow.II.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.TLow.II.Unif[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

set.seed(123)
a.vec <- rlnorm(1000, mean = log(0.477), sd = log(2)) 
h.vec <- rlnorm(1000, mean = log(0.038), sd = log(2)) 
Ex2.TLow.II.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.TLow.II.Norm[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 2, Low Treatment: Rogers' Type II FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 50))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.TLow.II.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 2, Low Treatment: Rogers' Type II FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 50))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.TLow.II.Norm[[i]][j])
  }
}
```

##### Hassell's Type III FR Model

```{r}
# Initial Densities

N0 <- c(2, 3, 5, 10, 20, 30, 50)

# Simulations

b.vec <- sample(seq(0.062, 197962.2481/100000, 0.001), 1000, replace = TRUE) 
c.vec <- sample(seq(0.000, 533631.8351/100000, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.000, 0.143, 0.001), 1000, replace = TRUE)
Ex2.TLow.III.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.TLow.III.Unif[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

b.vec <- rlnorm(1000, mean = log(0.191), sd = log(2))
c.vec <- rlnorm(1000, mean = log(0.239), sd = log(2))
h.vec <- rlnorm(1000, mean = log(0.061), sd = log(2))
Ex2.TLow.III.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.TLow.III.Norm[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 2, Low Treatment: Hassell's Type III FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 60))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.TLow.III.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 2, Low Treatment: Hassell's Type III FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 60))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.TLow.III.Norm[[i]][j])
  }
}
```

#### Treatment: Medium

##### Rogers' Type II FR Model

[***NA***]{.underline}

##### Hassell's Type III FR Model

```{r}
# Initial Densities

N0 <- c(2, 3, 5, 10, 20, 30, 50)

# Simulations

b.vec <- sample(seq(0.013, 323804.821/100000, 0.001), 1000, replace = TRUE) 
c.vec <- sample(seq(0.000, 3514096.291/100000, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.000, 0.274, 0.001), 1000, replace = TRUE)
Ex2.TMed.III.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.TMed.III.Unif[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

b.vec <- rlnorm(1000, mean = log(0.039), sd = log(2))
c.vec <- rlnorm(1000, mean = log(0.180), sd = log(2))
h.vec <- rlnorm(1000, mean = log(0.067), sd = log(2))
Ex2.TMed.III.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.TMed.III.Norm[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 2, Medium Treatment: Hassell's Type III FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 60))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.TMed.III.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 2, Medium Treatment: Hassell's Type III FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 60))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.TMed.III.Norm[[i]][j])
  }
}
```

#### Treatment: High

##### Rogers' Type II FR Model

```{r}
# Initial Densities

N0 <- c(2, 3, 5, 10, 20, 30, 50)

# Simulations

a.vec <- sample(seq(0.086, 0.207, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.000, 0.257, 0.001), 1000, replace = TRUE)
Ex2.THigh.II.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.THigh.II.Unif[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

a.vec <- rlnorm(1000, mean = log(0.144), sd = log(2)) 
h.vec <- rlnorm(1000, mean = log(0.046), sd = log(2)) 
Ex2.THigh.II.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.THigh.II.Norm[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 2, High Treatment: Rogers' Type II FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 20))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.THigh.II.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 2, High Treatment: Rogers' Type II FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 50))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.THigh.II.Norm[[i]][j])
  }
}
```

##### Hassell's Type III FR Model

```{r}
# Initial Densities

N0 <- c(2, 3, 5, 10, 20, 30, 50)

# Simulations

b.vec <- sample(seq(0.010, 0.068, 0.001), 1000, replace = TRUE) 
c.vec <- sample(seq(0.000, 2.007, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.000, 0.420, 0.001), 1000, replace = TRUE)
Ex2.THigh.III.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.THigh.III.Unif[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

b.vec <- rlnorm(1000, mean = log(0.024), sd = log(2))
c.vec <- rlnorm(1000, mean = log(0.026), sd = log(2))
h.vec <- rlnorm(1000, mean = log(0.181), sd = log(2))
Ex2.THigh.III.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex2.THigh.III.Norm[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 2, High Treatment: Hassell's Type III FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 45))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.THigh.III.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 2, High Treatment: Hassell's Type III FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 50), ylim = c(0, 45))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex2.THigh.III.Norm[[i]][j])
  }
}
```

### Experiment #3

#### Treatment: Rocks

##### Rogers' Type II FR Model

```{r}
# Initial Densities

N0 <- c(2, 3, 5, 10, 20, 30)

# Simulations

a.vec <- sample(seq(0.075, 0.211, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.000, 0.293, 0.001), 1000, replace = TRUE)
Ex3.TRocks.II.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex3.TRocks.II.Unif[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

a.vec <- rlnorm(1000, mean = log(0.131), sd = log(2)) 
h.vec <- rlnorm(1000, mean = log(0.102), sd = log(2)) 
Ex3.TRocks.II.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex3.TRocks.II.Norm[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 3, Rocks Treatment: Rogers' Type II FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 30), ylim = c(0, 20))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex3.TRocks.II.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 3, Rocks Treatment: Rogers' Type II FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 30), ylim = c(0, 20))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex3.TRocks.II.Norm[[i]][j])
  }
}
```

##### Hassell's Type III FR Model

[***NA***]{.underline}

#### Treatment: Sand

##### Rogers' Type II FR Model

```{r}
# Initial Densities

N0 <- c(2, 3, 5, 10, 20, 30)

# Simulations

a.vec <- sample(seq(0.488, 1.516, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.000, 0.249, 0.001), 1000, replace = TRUE)
Ex3.TSand.II.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex3.TSand.II.Unif[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

a.vec <- rlnorm(1000, mean = log(0.848), sd = log(2)) 
h.vec <- rlnorm(1000, mean = log(0.048), sd = log(2)) 
Ex3.TSand.II.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex3.TSand.II.Norm[[i]][j] <- round(RogersII(N0[i], a.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 3, Sand Treatment: Rogers' Type II FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 30), ylim = c(0, 35))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex3.TSand.II.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 3, Sand Treatment: Rogers' Type II FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 30), ylim = c(0, 35))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex3.TSand.II.Norm[[i]][j])
  }
}
```

##### Hassell's Type III FR Model

```{r}
# Initial Densities

N0 <- c(2, 3, 5, 10, 20, 30)

# Simulations

b.vec <- sample(seq(0.221, 3338468.210/1000000, 0.001), 1000, replace = TRUE) 
c.vec <- sample(seq(0.000, 1780576.771/1000000, 0.001), 1000, replace = TRUE) 
h.vec <- sample(seq(0.000, 0.289, 0.001), 1000, replace = TRUE)
Ex3.TSand.III.Unif <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex3.TSand.III.Unif[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

b.vec <- rlnorm(1000, mean = log(1.181), sd = log(2))
c.vec <- rlnorm(1000, mean = log(1.163), sd = log(2))
h.vec <- rlnorm(1000, mean = log(0.058), sd = log(2))
Ex3.TSand.III.Norm <- vector(mode = 'list', length = length(N0))
for (i in 1:length(N0)){
  for (j in 1:1000){
    Ex3.TSand.III.Norm[[i]][j] <- round(HassellIII(N0[i], b.vec[j], c.vec[j], h.vec[j], 2))
  }
}

# Plotting

plot(1, type = "n", main = "Experiment 1, Sand Treatment: Hassell's Type III FR | Unif", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 30), ylim = c(0, 30))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex3.TSand.III.Unif[[i]][j])
  }
}

plot(1, type = "n", main = "Experiment 1, Sand Treatment: Hassell's Type III FR | Norm", xlab = "Initial Prey Density", ylab = "Number of Prey Eaten", xlim = c(0, 30), ylim = c(0, 30))
for (i in 1:length(N0)){
  for (j in 1:1000){
    points(x = N0[i], y = Ex3.TSand.III.Norm[[i]][j])
  }
}
```

## Model Fitting and Selection

**Data Structure:**

-   All the simulated data are stored in lists. Each list is named by experiment ("Ex"), treatment ("T"), functional response model ("II" or "III"), and sampling distribution ("Unif" or "Norm"). For example: "Ex1.TLow.III.Norm" denotes (1) Experiment 1, (2) Low Treatment, (3) Type III FR, (4) from a normal distribution.

-   Each list is of equal length to the number of initial prey densities used in the experiments (or, here, the length of the vector, $N_0$).

-   Each listen item contains a vector of length 1000. Each of these 1000 values is the output ($N_e$) of a single simulation.

### Changing Data Structure (Idiot Time)

#### Experiment 1

```{r}
N0 <- rep(c(4, 6, 10, 20, 60, 90, 120), times = 1000)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.TLow.II.Unif[[1]][i], 
              Ex1.TLow.II.Unif[[2]][i], 
              Ex1.TLow.II.Unif[[3]][i], 
              Ex1.TLow.II.Unif[[4]][i], 
              Ex1.TLow.II.Unif[[5]][i], 
              Ex1.TLow.II.Unif[[6]][i], 
              Ex1.TLow.II.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TLow.II.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.TLow.II.Norm[[1]][i], 
              Ex1.TLow.II.Norm[[2]][i], 
              Ex1.TLow.II.Norm[[3]][i], 
              Ex1.TLow.II.Norm[[4]][i], 
              Ex1.TLow.II.Norm[[5]][i], 
              Ex1.TLow.II.Norm[[6]][i], 
              Ex1.TLow.II.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TLow.II.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.TMed.II.Unif[[1]][i], 
              Ex1.TMed.II.Unif[[2]][i], 
              Ex1.TMed.II.Unif[[3]][i], 
              Ex1.TMed.II.Unif[[4]][i], 
              Ex1.TMed.II.Unif[[5]][i], 
              Ex1.TMed.II.Unif[[6]][i], 
              Ex1.TMed.II.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TMed.II.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.TMed.II.Norm[[1]][i], 
              Ex1.TMed.II.Norm[[2]][i], 
              Ex1.TMed.II.Norm[[3]][i], 
              Ex1.TMed.II.Norm[[4]][i], 
              Ex1.TMed.II.Norm[[5]][i], 
              Ex1.TMed.II.Norm[[6]][i], 
              Ex1.TMed.II.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TMed.II.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.TMed.III.Unif[[1]][i], 
              Ex1.TMed.III.Unif[[2]][i], 
              Ex1.TMed.III.Unif[[3]][i], 
              Ex1.TMed.III.Unif[[4]][i], 
              Ex1.TMed.III.Unif[[5]][i], 
              Ex1.TMed.III.Unif[[6]][i], 
              Ex1.TMed.III.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TMed.III.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.TMed.III.Norm[[1]][i], 
              Ex1.TMed.III.Norm[[2]][i], 
              Ex1.TMed.III.Norm[[3]][i], 
              Ex1.TMed.III.Norm[[4]][i], 
              Ex1.TMed.III.Norm[[5]][i], 
              Ex1.TMed.III.Norm[[6]][i], 
              Ex1.TMed.III.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TMed.III.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.THigh.II.Unif[[1]][i], 
              Ex1.THigh.II.Unif[[2]][i], 
              Ex1.THigh.II.Unif[[3]][i], 
              Ex1.THigh.II.Unif[[4]][i], 
              Ex1.THigh.II.Unif[[5]][i], 
              Ex1.THigh.II.Unif[[6]][i], 
              Ex1.THigh.II.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; THigh.II.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.THigh.II.Norm[[1]][i], 
              Ex1.THigh.II.Norm[[2]][i], 
              Ex1.THigh.II.Norm[[3]][i], 
              Ex1.THigh.II.Norm[[4]][i], 
              Ex1.THigh.II.Norm[[5]][i], 
              Ex1.THigh.II.Norm[[6]][i], 
              Ex1.THigh.II.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; THigh.II.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.THigh.III.Unif[[1]][i], 
              Ex1.THigh.III.Unif[[2]][i], 
              Ex1.THigh.III.Unif[[3]][i], 
              Ex1.THigh.III.Unif[[4]][i], 
              Ex1.THigh.III.Unif[[5]][i], 
              Ex1.THigh.III.Unif[[6]][i], 
              Ex1.THigh.III.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; THigh.III.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex1.THigh.III.Norm[[1]][i], 
              Ex1.THigh.III.Norm[[2]][i], 
              Ex1.THigh.III.Norm[[3]][i], 
              Ex1.THigh.III.Norm[[4]][i], 
              Ex1.THigh.III.Norm[[5]][i], 
              Ex1.THigh.III.Norm[[6]][i], 
              Ex1.THigh.III.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; THigh.III.Norm <- data.frame(Ne, N0)

Ex1SimDat <- list(TLow.II.Unif, TLow.II.Norm,
                  TMed.II.Unif, TMed.II.Norm, TMed.III.Unif, TMed.III.Norm,
                  THigh.II.Unif, THigh.II.Norm, THigh.III.Unif, THigh.III.Norm)
names(Ex1SimDat) <- c("TLow.II.Unif", "TLow.II.Norm",
                      "TMed.II.Unif", "TMed.II.Norm", "TMed.III.Unif", "TMed.III.Norm",
                      "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")
```

#### Experiment 2

```{r}
N0 <- rep(c(2, 3, 5, 10, 20, 30, 50), times = 1000)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.TLow.II.Unif[[1]][i], 
              Ex2.TLow.II.Unif[[2]][i], 
              Ex2.TLow.II.Unif[[3]][i], 
              Ex2.TLow.II.Unif[[4]][i], 
              Ex2.TLow.II.Unif[[5]][i], 
              Ex2.TLow.II.Unif[[6]][i], 
              Ex2.TLow.II.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TLow.II.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.TLow.II.Norm[[1]][i], 
              Ex2.TLow.II.Norm[[2]][i], 
              Ex2.TLow.II.Norm[[3]][i], 
              Ex2.TLow.II.Norm[[4]][i], 
              Ex2.TLow.II.Norm[[5]][i], 
              Ex2.TLow.II.Norm[[6]][i], 
              Ex2.TLow.II.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TLow.II.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.TLow.III.Unif[[1]][i], 
              Ex2.TLow.III.Unif[[2]][i], 
              Ex2.TLow.III.Unif[[3]][i], 
              Ex2.TLow.III.Unif[[4]][i], 
              Ex2.TLow.III.Unif[[5]][i], 
              Ex2.TLow.III.Unif[[6]][i], 
              Ex2.TLow.III.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TLow.III.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.TLow.III.Norm[[1]][i], 
              Ex2.TLow.III.Norm[[2]][i], 
              Ex2.TLow.III.Norm[[3]][i], 
              Ex2.TLow.III.Norm[[4]][i], 
              Ex2.TLow.III.Norm[[5]][i], 
              Ex2.TLow.III.Norm[[6]][i], 
              Ex2.TLow.III.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TLow.III.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.TMed.III.Unif[[1]][i], 
              Ex2.TMed.III.Unif[[2]][i], 
              Ex2.TMed.III.Unif[[3]][i], 
              Ex2.TMed.III.Unif[[4]][i], 
              Ex2.TMed.III.Unif[[5]][i], 
              Ex2.TMed.III.Unif[[6]][i], 
              Ex2.TMed.III.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TMed.III.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.TMed.III.Norm[[1]][i], 
              Ex2.TMed.III.Norm[[2]][i], 
              Ex2.TMed.III.Norm[[3]][i], 
              Ex2.TMed.III.Norm[[4]][i], 
              Ex2.TMed.III.Norm[[5]][i], 
              Ex2.TMed.III.Norm[[6]][i], 
              Ex2.TMed.III.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; TMed.III.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.THigh.II.Unif[[1]][i], 
              Ex2.THigh.II.Unif[[2]][i], 
              Ex2.THigh.II.Unif[[3]][i], 
              Ex2.THigh.II.Unif[[4]][i], 
              Ex2.THigh.II.Unif[[5]][i], 
              Ex2.THigh.II.Unif[[6]][i], 
              Ex2.THigh.II.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; THigh.II.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.THigh.II.Norm[[1]][i], 
              Ex2.THigh.II.Norm[[2]][i], 
              Ex2.THigh.II.Norm[[3]][i], 
              Ex2.THigh.II.Norm[[4]][i], 
              Ex2.THigh.II.Norm[[5]][i], 
              Ex2.THigh.II.Norm[[6]][i], 
              Ex2.THigh.II.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; THigh.II.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.THigh.III.Unif[[1]][i], 
              Ex2.THigh.III.Unif[[2]][i], 
              Ex2.THigh.III.Unif[[3]][i], 
              Ex2.THigh.III.Unif[[4]][i], 
              Ex2.THigh.III.Unif[[5]][i], 
              Ex2.THigh.III.Unif[[6]][i], 
              Ex2.THigh.III.Unif[[7]][i])
  Ne <- c(Ne, NeTemp)
}; THigh.III.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex2.THigh.III.Norm[[1]][i], 
              Ex2.THigh.III.Norm[[2]][i], 
              Ex2.THigh.III.Norm[[3]][i], 
              Ex2.THigh.III.Norm[[4]][i], 
              Ex2.THigh.III.Norm[[5]][i], 
              Ex2.THigh.III.Norm[[6]][i], 
              Ex2.THigh.III.Norm[[7]][i])
  Ne <- c(Ne, NeTemp)
}; THigh.III.Norm <- data.frame(Ne, N0)

Ex2SimDat <- list(TLow.II.Unif, TLow.II.Norm, TLow.III.Unif, TLow.III.Norm,
                  TMed.III.Unif, TMed.III.Norm,
                  THigh.II.Unif, THigh.II.Norm, THigh.III.Unif, THigh.III.Norm)
names(Ex2SimDat) <- c("TLow.II.Unif", "TLow.II.Norm", "TLow.III.Unif", "TLow.III.Norm",
                      "TMed.III.Unif", "TMed.III.Norm",
                      "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")
```

#### Experiment 3

```{r}
N0 <- rep(c(2, 3, 5, 10, 20, 30), times = 1000)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex3.TRocks.II.Unif[[1]][i], 
              Ex3.TRocks.II.Unif[[2]][i], 
              Ex3.TRocks.II.Unif[[3]][i], 
              Ex3.TRocks.II.Unif[[4]][i], 
              Ex3.TRocks.II.Unif[[5]][i], 
              Ex3.TRocks.II.Unif[[6]][i])
  Ne <- c(Ne, NeTemp)
}; TRocks.II.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex3.TRocks.II.Norm[[1]][i], 
              Ex3.TRocks.II.Norm[[2]][i], 
              Ex3.TRocks.II.Norm[[3]][i], 
              Ex3.TRocks.II.Norm[[4]][i], 
              Ex3.TRocks.II.Norm[[5]][i], 
              Ex3.TRocks.II.Norm[[6]][i])
  Ne <- c(Ne, NeTemp)
}; TRocks.II.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex3.TSand.II.Unif[[1]][i], 
              Ex3.TSand.II.Unif[[2]][i], 
              Ex3.TSand.II.Unif[[3]][i], 
              Ex3.TSand.II.Unif[[4]][i], 
              Ex3.TSand.II.Unif[[5]][i], 
              Ex3.TSand.II.Unif[[6]][i])
  Ne <- c(Ne, NeTemp)
}; TSand.II.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex3.TSand.II.Norm[[1]][i], 
              Ex3.TSand.II.Norm[[2]][i], 
              Ex3.TSand.II.Norm[[3]][i], 
              Ex3.TSand.II.Norm[[4]][i], 
              Ex3.TSand.II.Norm[[5]][i], 
              Ex3.TSand.II.Norm[[6]][i])
  Ne <- c(Ne, NeTemp)
}; TSand.II.Norm <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex3.TSand.III.Unif[[1]][i], 
              Ex3.TSand.III.Unif[[2]][i], 
              Ex3.TSand.III.Unif[[3]][i], 
              Ex3.TSand.III.Unif[[4]][i], 
              Ex3.TSand.III.Unif[[5]][i], 
              Ex3.TSand.III.Unif[[6]][i])
  Ne <- c(Ne, NeTemp)
}; TSand.III.Unif <- data.frame(Ne, N0)

Ne <- c()
for (i in 1:1000){
  NeTemp <- c(Ex3.TSand.III.Norm[[1]][i], 
              Ex3.TSand.III.Norm[[2]][i], 
              Ex3.TSand.III.Norm[[3]][i], 
              Ex3.TSand.III.Norm[[4]][i], 
              Ex3.TSand.III.Norm[[5]][i], 
              Ex3.TSand.III.Norm[[6]][i])
  Ne <- c(Ne, NeTemp)
}; TSand.III.Norm <- data.frame(Ne, N0)

Ex3SimDat <- list(TRocks.II.Unif, TRocks.II.Norm,
                  TSand.II.Unif, TSand.II.Norm, TSand.III.Unif, TSand.III.Norm)
names(Ex3SimDat) <- c("TRocks.II.Unif", "TRocks.II.Norm",
                      "TSand.II.Unif", "TSand.II.Norm", "TSand.III.Unif", "TSand.III.Norm")
```

### Method (1): Juliano's

Writing the function to sort outcomes.

```{r}
getType.Juliano <- function(x) {
  stopifnot(inherits(x, "frtest"))

  T2Coef <- coef(summary(x$modT2))
  T2CoefOut <- T2Coef[2, ] |> matrix(nrow = 1)
  
  T3Coef <- coef(summary(x$modT3))
  T3CoefOut <- T3Coef[2:3, ]
  
  Type <- if(T2CoefOut[1, 1] < 0 & T2CoefOut[1, 4] < 0.05) {
    "type-II response"
  } else if (T3CoefOut[1, 1] > 0 & 
             T3CoefOut[1, 4] < 0.05 & 
             T3CoefOut[2, 1] < 0 & 
             T3CoefOut[2, 4] < 0.05) {
    "type-III response"
  }
  else {
    "No evidence for any response."
  }
  Type
}
```

#### One Test Per Row

```{r}
## Experiment 1
N0 <- c(4, 6, 10, 20, 60, 90, 120)
Out.List.Outer <-  vector(mode = 'list', length = length(Ex1SimDat)) 
suppressWarnings({
for (i in 1:length(Ex1SimDat)){
  Out.List.Inner <-  vector(mode = 'list', length = 1000)
  m <- 1; n <- 7
  for (j in 1:1000){
    SimDat <- Ex1SimDat[[i]][m:n, ]
    Output <- frair_test(formula = Ne ~ N0, data = SimDat)
    Out.List.Inner[[j]] <- Output
    m <- m + 7; n <- n + 7
  }
  Out.List.Outer[[i]] <- Out.List.Inner
}})
Ex1.Prop <- c() 
for (i in 1:length(Ex1SimDat)){
  Temp <- c(lapply(Out.List.Outer[[i]], getType.Juliano))
  II.III.NA <- c(length(which(Temp == "type-II response")),
                 length(which(Temp == "type-III response")),
                 length(which(Temp == "No evidence for any response.")))
  Ex1.Prop <- rbind(Ex1.Prop, II.III.NA)
}
colnames(Ex1.Prop) <- c("II", "III", "NA")
rownames(Ex1.Prop) <- c("TLow.II.Unif", "TLow.II.Norm",
                        "TMed.II.Unif", "TMed.II.Norm", "TMed.III.Unif", "TMed.III.Norm",
                        "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")

## Experiment 2
N0 <- c(2, 3, 5, 10, 20, 30, 50)
Out.List.Outer <-  vector(mode = 'list', length = length(Ex2SimDat)) 
suppressWarnings({
for (i in 1:length(Ex2SimDat)){
  Out.List.Inner <-  vector(mode = 'list', length = 1000)
  m <- 1; n <- 7
  for (j in 1:1000){
    SimDat <- Ex2SimDat[[i]][m:n, ]
    SimDat <- SimDat %>% replace(is.na(.), 0) # Gives no response
    Output <- frair_test(formula = Ne ~ N0, data = SimDat)
    Out.List.Inner[[j]] <- Output
    m <- m + 7; n <- n + 7
  }
  Out.List.Outer[[i]] <- Out.List.Inner
}})
Ex2.Prop <- c() 
for (i in 1:length(Ex2SimDat)){
  Temp <- c(lapply(Out.List.Outer[[i]], getType.Juliano))
  II.III.NA <- c(length(which(Temp == "type-II response")),
                 length(which(Temp == "type-III response")),
                 length(which(Temp == "No evidence for any response.")))
  Ex2.Prop <- rbind(Ex2.Prop, II.III.NA)
}
colnames(Ex2.Prop) <- c("II", "III", "NA")
rownames(Ex2.Prop) <- c("TLow.II.Unif", "TLow.II.Norm", "TLow.III.Unif", "TLow.III.Norm",
                        "TMed.III.Unif", "TMed.III.Norm",
                        "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")

## Experiment 3
N0 <- c(2, 3, 5, 10, 20, 30)
Out.List.Outer <-  vector(mode = 'list', length = length(Ex3SimDat)) 
suppressWarnings({
for (i in 1:length(Ex3SimDat)){
  Out.List.Inner <-  vector(mode = 'list', length = 1000)
  m <- 1; n <- 6
  for (j in 1:1000){
    SimDat <- Ex3SimDat[[i]][m:n, ]
    SimDat <- SimDat %>% replace(is.na(.), 0) # Gives no response
    Output <- frair_test(formula = Ne ~ N0, data = SimDat)
    Out.List.Inner[[j]] <- Output
    m <- m + 6; n <- n + 6
  }
  Out.List.Outer[[i]] <- Out.List.Inner
}})
Ex3.Prop <- c() 
for (i in 1:length(Ex3SimDat)){
  Temp <- c(lapply(Out.List.Outer[[i]], getType.Juliano))
  II.III.NA <- c(length(which(Temp == "type-II response")),
                 length(which(Temp == "type-III response")),
                 length(which(Temp == "No evidence for any response.")))
  Ex3.Prop <- rbind(Ex3.Prop, II.III.NA)
}
colnames(Ex3.Prop) <- c("II", "III", "NA")
rownames(Ex3.Prop) <- c("TRocks.II.Unif", "TRocks.II.Norm",
                        "TSand.II.Unif", "TSand.II.Norm", "TSand.III.Unif", "TSand.III.Norm")

## SAVING OUTPUTS
saveRDS(Ex1.Prop, here("./SimOutputs/Ex1Prop_Juliano.rds"))
saveRDS(Ex2.Prop, here("./SimOutputs/Ex2Prop_Juliano.rds"))
saveRDS(Ex3.Prop, here("./SimOutputs/Ex3Prop_Juliano.rds"))
```

#### Summarising Results

```{r}
Ex1.Prop <- readRDS(here("./SimOutputs/Ex1Prop_Juliano.rds"))
Ex2.Prop <- readRDS(here("./SimOutputs/Ex2Prop_Juliano.rds"))
Ex3.Prop <- readRDS(here("./SimOutputs/Ex3Prop_Juliano.rds"))

## Experiment 1
Cases <- c("TLow.II.Unif", "TLow.II.Norm",
           "TMed.II.Unif", "TMed.II.Norm", "TMed.III.Unif", "TMed.III.Norm",
           "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")
par(mar = c(8, 5, 4, 3))
plot(x = 1:10, y = as.numeric(Ex1.Prop[ ,1]), col = "orchid", pch = c(8, 8, 8, 8, 19, 19, 8, 8, 19, 19), 
     main = "Experiment 1", xlab = "", ylab = "Number of Simulations (/1000)",
     ylim = c(0, 1000), xaxt = "n")
points(x = 1:10, y = as.numeric(Ex1.Prop[ ,2]), col = "cornflowerblue", pch = c(19, 19, 19, 19, 8, 8, 19, 19, 8, 8))
points(x = 1:10, y = as.numeric(Ex1.Prop[ ,3]), col = "goldenrod2", pch = 19)
axis(1, at = 1:10, labels = Cases, las = 2)

## Experiment 2
Cases <- c("TLow.II.Unif", "TLow.II.Norm", "TLow.III.Unif", "TLow.III.Norm",
           "TMed.III.Unif", "TMed.III.Norm",
           "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")
par(mar = c(8, 5, 4, 3))
plot(x = 1:10, y = as.numeric(Ex2.Prop[ ,1]), col = "orchid", pch = c(8, 8, 19, 19, 19, 19, 8, 8, 19, 19), 
     main = "Experiment 2", xlab = "", ylab = "Number of Simulations (/1000)",
     ylim = c(0, 1000), xaxt = "n")
points(x = 1:10, y = as.numeric(Ex2.Prop[ ,2]), col = "cornflowerblue", pch = c(19, 19, 8, 8, 8, 8, 19, 19, 8, 8))
points(x = 1:10, y = as.numeric(Ex2.Prop[ ,3]), col = "goldenrod2", pch = 19)
axis(1, at = 1:10, labels = Cases, las = 2)

## Experiment 3
Cases <- c("TRocks.II.Unif", "TRocks.II.Norm",
           "TSand.II.Unif", "TSand.II.Norm", "TSand.III.Unif", "TSand.III.Norm")
par(mar = c(8, 5, 4, 3))
plot(x = 1:6, y = as.numeric(Ex3.Prop[ ,1]), col = "orchid", pch = c(8, 8, 8, 8, 19, 19), 
     main = "Experiment 3", xlab = "", ylab = "Number of Simulations (/1000)",
     ylim = c(0, 1000), xaxt = "n")
points(x = 1:6, y = as.numeric(Ex3.Prop[ ,2]), col = "cornflowerblue", pch = c(19, 19, 19, 19, 8, 8))
points(x = 1:6, y = as.numeric(Ex3.Prop[ ,3]), col = "goldenrod2", pch = 19)
axis(1, at = 1:6, labels = Cases, las = 2)
```

### Method (2): Generalized FR w/ Scaling Exponent

Writing the function to sort outcomes.

```{r}
getType.FlexFR <- function(x){
  stopifnot(inherits(x, "frfit"))
  Pr <- coef(summary(x$fit))[2, 4]
  Type <- if(is.na(Pr)) {
    "No evidence for any response."
  } else if (Pr <= 0.05) {
    "type-II response"
  } else {
    "type-III response"
  }
  Type
}
```

#### One Test Per Row

```{r}
## Experiment 1
N0 <- c(4, 6, 10, 20, 60, 90, 120)
Out.List.Outer <-  vector(mode = 'list', length = length(Ex1SimDat)) 
suppressWarnings({
for (i in 1:length(Ex1SimDat)){
  Out.List.Inner <-  vector(mode = 'list', length = 1000)
  m <- 1; n <- 7
  for (j in 1:1000){
    SimDat <- Ex1SimDat[[i]][m:n, ]
    Output <- frair_fit(formula = Ne ~ N0, data = SimDat, response = "flexpnr",
                        start = list(b = 0.5, q = 0, h= 0.5), fixed = list(T = 6))
    Out.List.Inner[[j]] <- Output
    m <- m + 7; n <- n + 7
  }
  Out.List.Outer[[i]] <- Out.List.Inner
}})
Ex1.Prop <- c() 
for (i in 1:length(Ex1SimDat)){
  Temp <- c(lapply(Out.List.Outer[[i]], getType.FlexFR))
  II.III.NA <- c(length(which(Temp == "type-II response")),
                 length(which(Temp == "type-III response")),
                 length(which(Temp == "No evidence for any response.")))
  Ex1.Prop <- rbind(Ex1.Prop, II.III.NA)
}
colnames(Ex1.Prop) <- c("II", "III", "NA")
rownames(Ex1.Prop) <- c("TLow.II.Unif", "TLow.II.Norm",
                        "TMed.II.Unif", "TMed.II.Norm", "TMed.III.Unif", "TMed.III.Norm",
                        "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")

## Experiment 2
N0 <- c(2, 3, 5, 10, 20, 30, 50)
Out.List.Outer <-  vector(mode = 'list', length = length(Ex2SimDat)) 
suppressWarnings({
for (i in 1:length(Ex2SimDat)){
  Out.List.Inner <-  vector(mode = 'list', length = 1000)
  m <- 1; n <- 7
  for (j in 1:1000){
    SimDat <- Ex2SimDat[[i]][m:n, ]
    SimDat <- SimDat %>% replace(is.na(.), 0) # Gives no response
    Output <- frair_fit(formula = Ne ~ N0, data = SimDat, response = "flexpnr",
                        start = list(b = 0.5, q = 0, h= 0.5), fixed = list(T = 6))
    Out.List.Inner[[j]] <- Output
    m <- m + 7; n <- n + 7
  }
  Out.List.Outer[[i]] <- Out.List.Inner
}})
Ex2.Prop <- c() 
for (i in 1:length(Ex2SimDat)){
  Temp <- c(lapply(Out.List.Outer[[i]], getType.FlexFR))
  II.III.NA <- c(length(which(Temp == "type-II response")),
                 length(which(Temp == "type-III response")),
                 length(which(Temp == "No evidence for any response.")))
  Ex2.Prop <- rbind(Ex2.Prop, II.III.NA)
}
colnames(Ex2.Prop) <- c("II", "III", "NA")
rownames(Ex2.Prop) <- c("TLow.II.Unif", "TLow.II.Norm", "TLow.III.Unif", "TLow.III.Norm",
                        "TMed.III.Unif", "TMed.III.Norm",
                        "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")

## Experiment 3
N0 <- c(2, 3, 5, 10, 20, 30)
Out.List.Outer <-  vector(mode = 'list', length = length(Ex3SimDat)) 
suppressWarnings({
for (i in 1:length(Ex3SimDat)){
  Out.List.Inner <-  vector(mode = 'list', length = 1000)
  m <- 1; n <- 6
  for (j in 1:1000){
    SimDat <- Ex3SimDat[[i]][m:n, ]
    SimDat <- SimDat %>% replace(is.na(.), 0) # Gives no response
    Output <- frair_fit(formula = Ne ~ N0, data = SimDat, response = "flexpnr",
                        start = list(b = 0.5, q = 0, h= 0.5), fixed = list(T = 6))
    Out.List.Inner[[j]] <- Output
    m <- m + 6; n <- n + 6
  }
  Out.List.Outer[[i]] <- Out.List.Inner
}})
Ex3.Prop <- c() 
for (i in 1:length(Ex3SimDat)){
  Temp <- c(lapply(Out.List.Outer[[i]], getType.FlexFR))
  II.III.NA <- c(length(which(Temp == "type-II response")),
                 length(which(Temp == "type-III response")),
                 length(which(Temp == "No evidence for any response.")))
  Ex3.Prop <- rbind(Ex3.Prop, II.III.NA)
}
colnames(Ex3.Prop) <- c("II", "III", "NA")
rownames(Ex3.Prop) <- c("TRocks.II.Unif", "TRocks.II.Norm",
                        "TSand.II.Unif", "TSand.II.Norm", "TSand.III.Unif", "TSand.III.Norm")

## SAVING OUTPUTS
saveRDS(Ex1.Prop, here("./SimOutputs/Ex1Prop_FlexFR.rds"))
saveRDS(Ex2.Prop, here("./SimOutputs/Ex2Prop_FlexFR.rds"))
saveRDS(Ex3.Prop, here("./SimOutputs/Ex3Prop_FlexFR.rds"))
```

#### Summarising Results

```{r}
Ex1.Prop <- readRDS(here("./SimOutputs/Ex1Prop_FlexFR.rds"))
Ex2.Prop <- readRDS(here("./SimOutputs/Ex2Prop_FlexFR.rds"))
Ex3.Prop <- readRDS(here("./SimOutputs/Ex3Prop_FlexFR.rds"))

## Experiment 1
Cases <- c("TLow.II.Unif", "TLow.II.Norm",
           "TMed.II.Unif", "TMed.II.Norm", "TMed.III.Unif", "TMed.III.Norm",
           "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")
par(mar = c(8, 5, 4, 3))
plot(x = 1:10, y = as.numeric(Ex1.Prop[ ,1]), col = "orchid", pch = c(8, 8, 8, 8, 19, 19, 8, 8, 19, 19), 
     main = "Experiment 1", xlab = "", ylab = "Number of Simulations (/1000)",
     ylim = c(0, 1000), xaxt = "n")
points(x = 1:10, y = as.numeric(Ex1.Prop[ ,2]), col = "cornflowerblue", pch = c(19, 19, 19, 19, 8, 8, 19, 19, 8, 8))
points(x = 1:10, y = as.numeric(Ex1.Prop[ ,3]), col = "goldenrod2", pch = 19)
axis(1, at = 1:10, labels = Cases, las = 2)

## Experiment 2
Cases <- c("TLow.II.Unif", "TLow.II.Norm", "TLow.III.Unif", "TLow.III.Norm",
           "TMed.III.Unif", "TMed.III.Norm",
           "THigh.II.Unif", "THigh.II.Norm", "THigh.III.Unif", "THigh.III.Norm")
par(mar = c(8, 5, 4, 3))
plot(x = 1:10, y = as.numeric(Ex2.Prop[ ,1]), col = "orchid", pch = c(8, 8, 19, 19, 19, 19, 8, 8, 19, 19), 
     main = "Experiment 2", xlab = "", ylab = "Number of Simulations (/1000)",
     ylim = c(0, 1000), xaxt = "n")
points(x = 1:10, y = as.numeric(Ex2.Prop[ ,2]), col = "cornflowerblue", pch = c(19, 19, 8, 8, 8, 8, 19, 19, 8, 8))
points(x = 1:10, y = as.numeric(Ex2.Prop[ ,3]), col = "goldenrod2", pch = 19)
axis(1, at = 1:10, labels = Cases, las = 2)

## Experiment 3
Cases <- c("TRocks.II.Unif", "TRocks.II.Norm",
           "TSand.II.Unif", "TSand.II.Norm", "TSand.III.Unif", "TSand.III.Norm")
par(mar = c(8, 5, 4, 3))
plot(x = 1:6, y = as.numeric(Ex3.Prop[ ,1]), col = "orchid", pch = c(8, 8, 8, 8, 19, 19), 
     main = "Experiment 3", xlab = "", ylab = "Number of Simulations (/1000)",
     ylim = c(0, 1000), xaxt = "n")
points(x = 1:6, y = as.numeric(Ex3.Prop[ ,2]), col = "cornflowerblue", pch = c(19, 19, 19, 19, 8, 8))
points(x = 1:6, y = as.numeric(Ex3.Prop[ ,3]), col = "goldenrod2", pch = 19)
axis(1, at = 1:6, labels = Cases, las = 2)
```

## Plotting Together

```{r}
Ex1.Prop.J <- readRDS(here("./SimOutputs/Ex1Prop_Juliano.rds"))
Ex1.Prop.F <- readRDS(here("./SimOutputs/Ex1Prop_FlexFR.rds"))

# Cases <- c("TLow.II.Unif", "TMed.II.Unif", "TMed.III.Unif", "THigh.II.Unif", "THigh.III.Unif")
# plot(x = 1:5, y = as.numeric(Ex1.Prop.J[c(1, 3, 5, 7, 9), 1]), col = alpha(c("forestgreen", "forestgreen", "red3", "forestgreen", "red3"), 0.2), pch = 19, cex = 2,
#      main = "Experiment 1", xlab = "", ylab = "Number of Simulations (/1000)",
#      ylim = c(0, 1000), xaxt = "n")
# points(x = 1:5, y = as.numeric(Ex1.Prop.J[c(1, 3, 5, 7, 9), 2]), col = alpha(c("red3", "red3", "forestgreen", "red3", "forestgreen"), 0.2), pch = 19, cex = 2)
# points(x = 1:5, y = as.numeric(Ex1.Prop.J[c(1, 3, 5, 7, 9), 3]), col = "grey", pch = 4, cex = 2)
# points(x = 1:5, y = as.numeric(Ex1.Prop.F[c(1, 3, 5, 7, 9), 1]), col = alpha(c("forestgreen", "forestgreen", "red3", "forestgreen", "red3"), 0.2), pch = 15, cex = 2)
# points(x = 1:5, y = as.numeric(Ex1.Prop.F[c(1, 3, 5, 7, 9), 2]), col = alpha(c("red3", "red3", "forestgreen", "red3", "forestgreen"), 0.2), pch = 15, cex = 2)
# points(x = 1:5, y = as.numeric(Ex1.Prop.F[c(1, 3, 5, 7, 9), 3]), col = "grey", pch = 4, cex = 2)
# axis(1, at = 1:5, labels = c("Low, II", "Med., II", "Med., III", "High, II", "High, III"))

Ex1.Unif.Js <- c(Ex1.Prop.J[1,1], Ex1.Prop.J[3,1], Ex1.Prop.J[5,2], Ex1.Prop.J[7,1], Ex1.Prop.J[9,2])
Ex1.Unif.Flex <- c(Ex1.Prop.F[1,1], Ex1.Prop.F[3,1], Ex1.Prop.F[5,2], Ex1.Prop.F[7,1], Ex1.Prop.F[9,2])
par(mar = c(5.1, 4.1, 4.1, 9.1), xpd = TRUE)
Cases <- c("TLow.II.Unif", "TMed.II.Unif", "TMed.III.Unif", "THigh.II.Unif", "THigh.III.Unif")
plot(x = 1:5, y = Ex1.Unif.Js, col = alpha("orchid", 0.4), pch = 19, cex = 2,
     main = "Experiment 1 (Draw from 'runif')", xlab = "", ylab = "Number of Simulations (/1000)",
     ylim = c(0, 1000), xaxt = "n")
points(x = 1:5, y = Ex1.Unif.Flex, col = alpha("goldenrod2", 0.4), pch = 19, cex = 2)
axis(1, at = 1:5, labels = c("Low, II", "Med., II", "Med., III", "High, II", "High, III"))
legend("topright", inset = c(-0.4, 0), legend = c("Juliano's", "Flexible FR"), col = c("orchid", "goldenrod2"), pch = 19)

Ex1.Unif.Js <- c(Ex1.Prop.J[2,1], Ex1.Prop.J[4,1], Ex1.Prop.J[6,2], Ex1.Prop.J[8,1], Ex1.Prop.J[10,2])
Ex1.Unif.Flex <- c(Ex1.Prop.F[2,1], Ex1.Prop.F[4,1], Ex1.Prop.F[6,2], Ex1.Prop.F[8,1], Ex1.Prop.F[10,2])
par(mar = c(5.1, 4.1, 4.1, 9.1), xpd = TRUE)
Cases <- c("TLow.II.Unif", "TMed.II.Unif", "TMed.III.Unif", "THigh.II.Unif", "THigh.III.Unif")
plot(x = 1:5, y = Ex1.Unif.Js, col = alpha("orchid", 0.4), pch = 19, cex = 2,
     main = "Experiment 1 (Draw from 'rnorm')", xlab = "", ylab = "Number of Simulations (/1000)",
     ylim = c(0, 1000), xaxt = "n")
points(x = 1:5, y = Ex1.Unif.Flex, col = alpha("goldenrod2", 0.4), pch = 19, cex = 2)
axis(1, at = 1:5, labels = c("Low, II", "Med., II", "Med., III", "High, II", "High, III"))
legend("topright", inset = c(-0.4, 0), legend = c("Juliano's", "Flexible FR"), col = c("orchid", "goldenrod2"), pch = 19)

Ex2.Prop.J <- readRDS("SimOutputs/Ex2Prop_Juliano.rds")
Ex2.Prop.F <- readRDS("SimOutputs/Ex2Prop_FlexFR.rds")
Ex3.Prop.J <- readRDS("SimOutputs/Ex3Prop_Juliano.rds")
Ex3.Prop.F <- readRDS("SimOutputs/Ex3Prop_FlexFR.rds")

```

### Method (4): Visual Inspection
